Insert the article title here

### 2020-07-23 tex/results.tex
join figures that goe in pairs

Effect of extended third dimension (in our case this is the y axis) are in Figures \ref{fig:ext_y_14a} and
\ref{fig:ext_y_14b}

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{ext_y_14a.pdf} 
    \caption{Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
    short edge configuration (electric field parallel to the shorter dimension)}
    \label{fig:ext_y_14a}
 \end{figure}

 \begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{ext_y_14b.pdf} 
    \caption{Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
    long edge configuration (electric field parallel to the longer dimension)}
    \label{fig:ext_y_14b}
 \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{tri_reg_round_14a.pdf} 
    \caption{Normalized (by max) Extinction cross section of a rectangle. Original trimesh, regular, and regular with 
    roundness. Short edge configuration (electric field parallel to the shorter dimension)}
    \label{fig:tri_reg_round_14a}
 \end{figure}

 \begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{tri_reg_round_14b.pdf} 
    \caption{Normalized (by max) Extinction cross section of a rectangle.  Original trimesh, regular, and regular with 
    roundness. Long edge configuration (electric field parallel to the longer dimension)}
    \label{fig:tri_reg_round_14b}
 \end{figure}

@@

 \begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{replication_14a.pdf} 
    \caption{Normalized (by max) Extinction cross section of a rectangle. Replication of 
    the short edge configuration (electric field parallel to the shorter dimension)}
    \label{fig:rep_14a}
 \end{figure}

 \begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{replication_14b.pdf} 
    \caption{Normalized (by max) Extinction cross section of a rectangle. Replication of the 
    long edge configuration (electric field parallel to the longer dimension)}
    \label{fig:rep_14b}
 \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{AR_22_vs_norm.pdf} 
    \caption{ Extinction cross section across wave number for SiC pillars of multiple Aspect ratios. 
             (H=950 nm, W=400nm, L=400-2800 (AR=1-7))
            Normalized by maximum extinction cross section as a function of wave number,
            for a pillar orientation such that the electric field is parallel polarized 
            (I HAVE TO EXPLAIN THIS BETTER, IT ALIGNS WITH THE LENGTH OF THE PILLAR). 
            We present the results for normal incidence and 22 degrees incidence, 
            for different aspect ratios (AR)
            }
    \label{fig:AR_22_vs_norm}
 \end{figure}

>>>>

Effect of extended third dimension (in our case this is the y axis) are in Figures \ref{fig:ext_y_14} and

\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{rockstuhl_rectangles.pdf} 
    \caption{Rockstuhl runs configurations}
    \label{fig:rectangle_sketch}
\end{figure}

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.45\textwidth]{ext_y_14a.pdf}}
    \subfloat{\includegraphics[width=0.45\textwidth]{ext_y_14b.pdf}} 
    %\caption{Extension of third dimension (y-axis) study for the case of rectangle prism of dimensions a=672 nm and b= 328 nm.
    %        Attempt of replication of Figure 14 a on Rockstuhl paper (case a1). In this case we have the constant 
    %        electric field parallel to the short dimension (b), and the geometry is in air. 
    %        Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
    %        short edge configuration (electric field parallel to the shorter dimension)}
    %\label{fig:ext_y_14a}
    %\label{fig:ext_y_14b}
    \caption{THIS IS A BIG CAPTION}
    \label{fig:ext_y_14}   
 \end{figure}

@@

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.45\textwidth]{tri_reg_round_14a.pdf}}
    \subfloat{\includegraphics[width=0.45\textwidth]{tri_reg_round_14b.pdf}}
    \caption{Normalized (by max) Extinction cross section of a rectangle. Original trimesh, regular, and regular with 
    roundness. Short edge configuration (electric field parallel to the shorter (left) dimension)}
    \label{fig:tri_reg_round_14}
 \end{figure}

@@

 \begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.45\textwidth]{replication_14a.pdf}}
    \subfloat{\includegraphics[width=0.45\textwidth]{replication_14b.pdf}}

    \caption{Normalized (by max) Extinction cross section of a rectangle. Replication of 
    the short (long) edge configuration (electric field parallel to the shorter (longer) dimension)}
    \label{fig:rep_14}
 \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{AR_22_vs_norm.pdf} 
    \caption{ Extinction cross section across wave number for SiC pillars of multiple Aspect ratios. 
             (H=950 nm, W=400nm, L=400-2800 (AR=1-7))
            Normalized by maximum extinction cross section as a function of wave number,
            for a pillar orientation such that the electric field is parallel polarized 
            (I HAVE TO EXPLAIN THIS BETTER, IT ALIGNS WITH THE LENGTH OF THE PILLAR). 
            We present the results for normal incidence and 22 degrees incidence, 
            for different aspect ratios (AR)
            }
    \label{fig:AR_22_vs_norm}
 \end{figure}
